Figures

### 2019-06-21 manuscript/figures.Rmd
specify correlation coefficients

```{r exploratory_dotplot, fig.cap = "Exploratory dotplots showing absolute value correlations.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/dotplot-1.pdf")
```

```{r exploratory_heatmap, fig.cap = "Exploratory heatmap showing absolute value correlations.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/08_exploratory_dotplot-1.pdf")
```

>>>>

```{r exploratory_dotplot, fig.cap = "Exploratory dotplots showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/dotplot-1.pdf")
```

```{r exploratory_heatmap, fig.cap = "Heatmap showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/08_exploratory_dotplot-1.pdf")
```
